---
title: "Proposal Presentation"
author: "Group Team 3<br> Calder, Ruairidh, Aarzu, Erblina"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(knitr)
library(xaringanthemer)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
top_500 <- read_csv(file = "data/top-500-movies.csv", col_types = cols(
  mpaa = col_factor(),
  genre = col_factor()
))
```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = "img/confetti.jpg"
)
```

class: inverse, center, middle

# The Data

---

# The Data
- We are using a dataset of the top 500 movies by production budget.
- The dataset was found [on Kaggle](https://www.kaggle.com/datasets/e0d29b8ab6ddedf4b39e4804768915ed8b5eb73dcd68bc6ef5b76aae6bf4d0ff)

- The dataset was collected by scraping [The Numbers website](https://www.the-numbers.com/movie/budgets/all)

- Each observation is a film

---
# The Variables
- `rank`: The ranking of the film by production budget.
- `title`: The title of the film.
- `url`: The link the film on the-numbers.com .
- `release_date`: The date the film was released.
- `production_cost`: The cost of producing the film (in USD).
- `domestic_gross`: The gross of the film in the US (in USD).
- `worldwide_gross`: The gross of the film worldwide (in USD).
- `opening_weekend`: The money made from sales in the opening weekend (in USD).
- `mpaa`: Age rating of the film.
- `genre`: The genre of the film.
- `theaters`: The maximum number of theaters showing the film at one time.
- `runtime`: The runtime of the film.
- `year`: The year the film released in.
---

# A glimpse of the data


``` {r data-glimpse, echo = FALSE}
glimpse(top_500)

```

---

class: inverse, center, middle

# The Question

---

class: center, middle

## How does opening weekend sales affect worldwide gross?

---
# How does opening weekend sales affect worldwide gross?

- Does high opening weekend sales (OWS) imply a high worldwide gross (WG)?

- Does genre affect the OWS/WG?

- What about age rating?



---

class: inverse, middle, center

# Data analysis plan

---

# Variables of Interest

- `rank`: We are going to use rank as an ID for each film, rather than how large its production budget was.

These can be used to compare how the opening weekend sales affect the worldwide gross.
- `opening_weekend`
- `worldwide_gross`

- We also use these to see how the age rating and genre affect both the opening weekend and the worldwide gross:
- `mpaa` and `genre`

---

# Preliminary Data Analysis
--

```{r top-genres, echo = FALSE, out.width = "50%", fig.width = 2}
top_genre <- top_500 %>%
  arrange(desc(worldwide_gross)) %>%
  slice(1:20) %>%
  group_by(genre)

top_genre %>% 
  ggplot(aes(x = genre)) +
  geom_bar() +
  coord_flip()
```
--
```{r top-age-rating, echo = FALSE, out.width = "50%", fig.width = 2}
top_age <- top_500 %>%
  arrange(desc(worldwide_gross)) %>%
  slice(1:20) %>%
  group_by(mpaa)


top_age %>%
  ggplot(aes(x = mpaa)) +
  geom_bar()

```

---

# Useful statistics

Some useful statistics would be the mean WG by genre and age rating, as this could help answer the question of how the genre and age rating affect the WG.

