---
title: "Proposal Presentation"
author: "Test Name<br> Calder, Ruairidh, Aarzu, Erblina"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(knitr)
library(xaringanthemer)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
top_500 <- read_csv(file = "data/top-500-movies.csv", col_types = cols(
  mpaa = col_factor(),
  genre = col_factor()
))
```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = "img/confetti.jpg"
)
```


class: inverse, center, middle

# The Question

---

class: center, middle

## How does opening weekend sales affect worldwide gross?

---
# How does opening weekend sales affect worldwide gross?

- Does high opening weekend sales (OWS) imply a high worldwide gross (WG)?

- Does genre affect the OWS/WG?

- What about age rating?

---

# The Data
- We are using a dataset of the top 500 movies by production budget.
- The dataset was found [on Kaggle](https://www.kaggle.com/datasets/e0d29b8ab6ddedf4b39e4804768915ed8b5eb73dcd68bc6ef5b76aae6bf4d0ff)

- The dataset was collected by scraping [The Numbers website](https://www.the-numbers.com/movie/budgets/all)

- Each observation is a film

---
# The Variables
- `rank`: The ranking of the film by production budget.
- `title`: The title of the film.
- `url`: The link the film on the-numbers.com .
- `release_date`: The date the film was released.
- `production_cost`: The cost of producing the film (in USD).
- `domestic_gross`: The gross of the film in the US (in USD).
- `worldwide_gross`: The gross of the film worldwide (in USD).
- `opening_weekend`: The money made from sales in the opening weekend (in USD).
- `mpaa`: Age rating of the film.
- `genre`: The genre of the film.
- `theaters`: The maximum number of theaters showing the film at one time.
- `runtime`: The runtime of the film.
- `year`: The year the film released in.
---

# The Data


``` {r data-glimpse, echo = FALSE}
glimpse(top_500)

```

---

class: inverse, middle, center

# Data analysis plan

---

# Variables of Interest

- `rank`: We are going to use rank as an ID for each film, rather than how large its production budget was.
- `opening_weekend`
- `worldwide_gross`
--
- We might also use:
- `mpaa` and `genre`

---

# Preliminary Data Analysis

```{r box-plot-opening}
ggplot(top_500,aes(x = opening_weekend)) +
  geom_boxplot()

```
--
```{r box-plot-worldwide}
ggplot(top_500, aes(x = worldwide_gross)) +
  geom_boxplot()
```

---

# Code

```{r boring-analysis}
# a boring analysis
#ave <- mean(cars$dist)
#print(ave)
```

---

# Plots

```{r recode-species, echo = FALSE}
# In this chunk I'm doing a bunch of analysis that I don't want to present 
# in my slides. But I need the resulting data frame for a plot I want to present.
#iris_modified <- iris %>%
  #mutate(Species = fct_other(Species, keep = "setosa"))
```

```{r plot-iris, echo = FALSE}
# Code hidden with echo = FALSE
# Uses modified iris dataset from previous chunk
# Play around with height and width until you're happy with the look
#ggplot(data = iris_modified, mapping = aes(x = Sepal.Width, y = Sepal.Length, color = Species)) +
  #geom_point() + 
  #theme_minimal() # theme options: https://ggplot2.tidyverse.org/reference/ggtheme.html
```

---

## Plot and text

.pull-left[
- Some text
- goes here
]
.pull-right[
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
#ggplot(penguins, aes(x = bill_length_mm, y = species, color = species)) +
#  geom_boxplot() +
  #theme_minimal()
```
]

---

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r iris-table, echo = FALSE}
#kable(head(iris), format = "html")
```

---

# Images

```{r castle, echo = FALSE, out.width = "60%", fig.align = "center", fig.cap = "Image credit: Photo by Jörg Angeli on Unsplash."}
include_graphics("https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80")
```

Or you can also include a full page image. See next slide.

---

background-image: url(https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80)

---

# Math Expressions

You can write LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\alpha+\beta$ renders $\alpha+\beta$. You can use the display style with double dollar signs:

```
$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
```

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

Limitations:

1. The source code of a LaTeX math expression must be in one line, unless it is inside a pair of double dollar signs, in which case the starting `$$` must appear in the very beginning of a line, followed immediately by a non-space character, and the ending `$$` must be at the end of a line, led by a non-space character;

1. There should not be spaces after the opening `$` or before the closing `$`.

1. Math does not work on the title slide (see [#61](https://github.com/yihui/xaringan/issues/61) for a workaround).

---

# Feeling adventurous?

- Want to find out more about `xaringan`? See https://slides.yihui.name/xaringan/#1.

- You are welcomed to use the default styling of the slides. In fact, that's what I expect majority of you will do. You will differentiate yourself with the content of your presentation.

- But some of you might want to play around with slide styling. The 
`xaringanthemer` provides some solutions for this that: https://pkg.garrickadenbuie.com/xaringanthemer.

- And if you want more bells and whistles, there is also `xaringanExtra`: https://pkg.garrickadenbuie.com/xaringanExtra.
